Global patterns of forest autotrophic carbon fluxes

### 2020-02-16 manuscript/manuscript draft.Rmd
updated manuscript draft to edit hypothesis table and reorder variables in table 2

```{r setup, include = FALSE}
# knitr::opts_knit$set(root.dir = 'C:/Users/gyrcbm/Dropbox/Global_Productivity/manuscript/')
knitr::opts_knit$set(root.dir = '/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/Global_Productivity/manuscript/')
```

@@

\renewcommand{\arraystretch}{2}
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, booktabs = TRUE, caption = "Summary of research questions, corresponding hypotheses, and results.'yes' indicates the hypothesis is supported, 'no' indicates the hypothesis is not supported, and 'n.s.' indicates that the relationship is not signficant.") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12) %>%
  pack_rows("Q1. How do FACF vary with latitude?", 1, 1, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Q2. How do FACF vary with MAT and MAP?", 2, 4, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Q3. How are FACF related to other climate variables?", 5, 7, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Q4. How does seasonality influence FACF?", 8, 11, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Q5. When standardised by growing season length, how do FACF vary with climate?", 12, 15, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  add_header_above(c(" ", " ", " ", "Forest autotrophic carbon fluxes (FACF)" = 9, " ")) %>%
  #column_spec(1, width = "15cm") %>%
  column_spec(2, width = "5cm") %>%
  column_spec(3:13, width = "1.8cm") %>%
  kableExtra::landscape()
```

@@

\newpage  
| Variable | Definition | Components included | Methodologies used | Number of records | Number of geographic areas |
|--------------|-------------------|-------------|------------------------|-------|-------|
| $GPP$ | Gross Primary Production | NA | flux partitioning of eddy-covariance; $NPP$+$R_{auto}$ | 243 | 49 |
| $NPP$ | Net Primary Production | stem, foliage, coarse root, fine root, optionally others (e.g., branch, reproductive, understory) | $ANPP$ + $BNPP$ (majority); $GPP$-$R_{auto}$ | 161 | 56 |
| $ANPP$ | Aboveground Net Primary Production | stem, foliage, optionally others (e.g., branch, reproductive, understory) |$ANPP_{woody-stem}$ + $ANPP_{foliage}$ (+ others) | 278 | 86 |
| $ANPP_{woody stem}$ | Woody stem growth component of $ANPP$ | woody stems down to DBH $\le$ 10cm (no branch turnover) | stem growth measurements scaled to biomass using allometries | 264 | 96 |
| $ANPP_{foliage}$ | Foliage component of $ANPP$ | foliage | litterfall collection (separated into components) | 98 | 49 |
| $BNPP$  | Belowground Net Primary Production | coarse and fine roots |  coarse roots estimated indirectly using allometries based on aboveground stem increment measures ; fine roots as below | 101 | 48 |
| $BNPP_{fine root}$ | Fine root component of $BNPP$ | fine roots | measurements combined one or more of the following: soil cores, minirhizotrons, turnover estimates,  root ingrowth cores | 88 | 41 |
| $R_{root}$ | Root Respiration | coarse and fine roots | partitioning of total soil respiration (e.g., through root exclusion), scaling of root gas exchange | 64 | 26 |
| $R_{auto}$ | Autotrophic Respiration | foliage, stem, and root | chamber measurements of component gas exchange | 22 | 13 |

>>>>

```{r setup, include = FALSE}
knitr::opts_knit$set(root.dir = 'C:/Users/becky/Dropbox (Smithsonian)/GitHub/Global_Productivity/manuscript/')
# knitr::opts_knit$set(root.dir = '/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/Global_Productivity/manuscript/')
```

@@

\renewcommand{\arraystretch}{2}
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
hypothesis_table[1,2] <- paste0(footnote_marker_number(1)," , ",footnote_marker_number(2)," , ", footnote_marker_number(3))
hypothesis_table[2,2] <- paste0(footnote_marker_number(4))
hypothesis_table[3,2] <- paste0(footnote_marker_number(1)," , ",footnote_marker_number(4))
hypothesis_table[4,2] <- paste0(footnote_marker_number(5))
hypothesis_table[10,2] <- paste0(footnote_marker_number(6)," , ",footnote_marker_number(7)," , ", footnote_marker_number(8))
hypothesis_table[11,2] <- paste0(footnote_marker_number(7)," , ", footnote_marker_number(8))
hypothesis_table[12,2] <- paste0(footnote_marker_number(8))
kable(hypothesis_table, booktabs = TRUE, caption = "Summary of research questions, corresponding hypotheses, and results. Statistically signficant support for/ rejection of hypotheses is indicated with 'yes'/'no', parentheses indicate partial overall support/rejection of hypotheses across all FACF, and '-' indicates no significant relationship.", escape = F) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12) %>%
  pack_rows("Q1. How do FACF vary with latitude?", 1, 1, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Q2. How do FACF vary with MAT and MAP?", 2, 4, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Q3. How are FACF related to other climate variables?", 5, 7, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Q4. How does seasonality influence FACF?", 8, 11, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("Q5. When standardised by growing season length, how do FACF vary with climate?", 12, 15, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  add_header_above(c(" ", " ", " ", "Forest autotrophic carbon fluxes (FACF)" = 9, " ")) %>%
  #column_spec(1, width = "15cm") %>%
  column_spec(2, width = "5cm") %>%
  column_spec(3:13, width = "1.8cm") %>%
  kableExtra::landscape() %>%
  kableExtra::footnote(number = c("Luyssaert et al. (2007)", "Gillman et al. (2015)", "Simova and Storch (2017)", "Schuur (2003)", "Taylor et al. (2016)", "Malhi (2012)", "Michaletz et al. (2014)", "Chu et al. (2016)"), footnote_as_chunk = TRUE)
```

@@

\newpage  
| Variable | Definition | Components included | Methodologies used | Number of records | Number of geographic areas |
|--------------|-------------------|-------------|------------------------|-------|-------|
| $GPP$ | Gross Primary Production | NA | flux partitioning of eddy-covariance; $NPP$+$R_{auto}$ | 243 | 49 |
| $NPP$ | Net Primary Production | stem, foliage, coarse root, fine root, optionally others (e.g., branch, reproductive, understory) | $ANPP$ + $BNPP$ (majority); $GPP$-$R_{auto}$ | 161 | 56 |
| $ANPP$ | Aboveground Net Primary Production | stem, foliage, optionally others (e.g., branch, reproductive, understory) |$ANPP_{woody-stem}$ + $ANPP_{foliage}$ (+ others) | 278 | 86 |
| $ANPP_{woody stem}$ | Woody stem growth component of $ANPP$ | woody stems down to DBH $\le$ 10cm (no branch turnover) | stem growth measurements scaled to biomass using allometries | 264 | 96 |
| $ANPP_{foliage}$ | Foliage component of $ANPP$ | foliage | litterfall collection (separated into components) | 98 | 49 |
| $BNPP$  | Belowground Net Primary Production | coarse and fine roots |  coarse roots estimated indirectly using allometries based on aboveground stem increment measures ; fine roots as below | 101 | 48 |
| $BNPP_{fine root}$ | Fine root component of $BNPP$ | fine roots | measurements combined one or more of the following: soil cores, minirhizotrons, turnover estimates,  root ingrowth cores | 88 | 41 |
| $R_{auto}$ | Autotrophic Respiration | foliage, stem, and root | chamber measurements of component gas exchange | 22 | 13 |
| $R_{root}$ | Root Respiration | coarse and fine roots | partitioning of total soil respiration (e.g., through root exclusion), scaling of root gas exchange | 64 | 26 |
